---
title: "pkgTemplateR - a vignette"
author: "John Smith"
date: "`r Sys.Date()`"
output: rmarkdown::pdf_document
toc: true
vignette: >
  %\VignetteIndexEntry{pkgTemplateR-package-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

\newpage

# Introduction

This R package does something useful... for sure...

```{r, include = FALSE}
# needed so that the as.data.frame part of the vignette
# does not need a restart of the session everytime the
# vignette is built
rm(list = ls())
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Installing from GitHub with `devtools`

Let's get started by installing the package straight from
[\textcolor{blue}{GitHub}](https://github.com/SwissClinicalTrialOrganisation/secuTrialR)
and then loading it. For this you will need to have `devtools` installed. We are
planning to add `secuTrialR` to CRAN but we are not there yet. If you are working on Windows and would
like to install with `devtools` you  will likely need to install
[\textcolor{blue}{Rtools}](https://cran.r-project.org/bin/windows/Rtools/).

\vspace{5pt}

```{r, eval = FALSE}
# install
devtools::install_github("CTU-Basel/pkgTemplateR")
```


# Loading the package

```{r}
# load
library(pkgTemplateR)
# show pkgTemplateR version
installed.packages()["pkgTemplateR", "Version"]
```

# Printing the contents of a text file

```{r}
path <- system.file("exdata", "file.txt",
                    package = "pkgTemplateR")
print_file_content(file_path = path)
```


\newpage
```{r}
sessionInfo()
```


